---
title: 'AP Statistics: Chapter 3 Exam Review'
author: "Alison Rector"
date: "2022-09-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
```

**In my meeting yesterday, I noticed that the number of people paying attention to the training was declining throughout the day. I collected the following data:**
Time (hours):      0  1 2 3 4 5 6
Number of people paying attention: 80 68 62 50 48 32 21

**1. Make a scatterplot of the data on your calculator and sketch it below.**  
```{r}
meeting_time<-c(0,1,2,3,4,5,6)
n_people<-c(80, 68, 62, 50, 48, 32, 21)

meeting_df<-data.frame(time=meeting_time, attention_n=n_people)
```

```{r}
library(ggplot2)
ggplot(data=meeting_df, aes(x=time, y=attention_n))+
  geom_point()+
  xlab("Time(hrs)")+
  ylab("Number ofPeople Paying Attention")+
  ggtitle("Attention During Meeting Data")
```


**2. Describe the data** (Direction, unusual features, form, strength)  
The data shows a strong negative linear relationship between time and the number of people paying attention during the training. There are no unusual features nor obvious outliers.  
**3. Find the line of best fit using the equations for a and b. Confirm that it matched with the calculator’s line of best fit.**  
```{r}
mymod<-lm(attention_n~time, data=meeting_df)
```
$N = 79.750-9.393*t$

**4. Make a prediction for the # of people paying attention at t = 2.5 hours.**
$N(2.5) = 79.750-9.393*(2.5) = 56.2675 \approx 56 \ people$
*5. What is r? Interpret.*
```{r}
cor(meeting_df$time, meeting_df$attention_n)
```

**6. What is r2? Interpret.**

```{r}
summary(mymod)
```
$r^2\approx0.9804$  
This means that approximately 98% of the variation in y can be explained by x.

**7. What is the slope of the LSRL? Interpret in the context of the problem.**
Every hour that passes there is a reduction of 9.39 people paying attention. 

**8. What is the y-intercept of the LSRL? Interpret in the context of the problem.**
79.750  
Approximately 80 people are paying attention at the start of the lecture.

**9. Identify the values a and b in the Minitab output:**
Predictor Coef SE Coeff T P
Constant 79.75 5.34 3.41 0
Time -9.393 4.23 -15.81 0
S = 3.143 R-Sq = 98.0% R-Sq (adj) = 97.2%

*10. Interpret s = 3.143 in the context of the problem.*  
This tells us that the regression model predicts the number of people who are paying attention during the training with an average error of about 3.143.  

*11. Find the residual for a time of 4 hours.*  
$\hat{y_4} = 79.750-9.393*(4) = 42.178$
${y_4} = 48$

$r_4 = (y_i -\hat{y}) = 48 - 42.178 = 5.822$

12. Make a residual plot on your calculator. Sketch it below.  



13. Mr. Bakri walked into the meeting at t = 7 hours and all of a sudden 82
people were paying attention. Would this point be influential? Prove it.
```{r}
meeting_time_new<-c(0,1,2,3,4,5,6, 7)
n_people_new<-c(80, 68, 62, 50, 48, 32, 21, 82)

meeting_df_new<-data.frame(time=meeting_time_new, attention_n=n_people_new)
```

```{r}
library(ggplot2)
ggplot(data=meeting_df_new, aes(x=time, y=attention_n))+
  geom_point()+
  xlab("Time(hrs)")+
  ylab("Number ofPeople Paying Attention")+
  ggtitle("Attention During Meeting Data")
```

```{r}
mymod<-lm(attention_n~time, data=meeting_df_new)
summary(mymod)
```
$N=68.417 -3.726t$

14. What would happen to r when we add this point.    
```{r}
cor(meeting_df_new$time, meeting_df_new$attention_n)
```

